Tail-indices and scale parameters of returns series

### 2017-04-04 papers/FX/draft.tex
In the process of merging Thomas' re-written introduction.

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage[bookmarks=true]{hyperref}
\usepackage{bookmark}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}

\usepackage{amssymb,amsmath,amsthm,amsfonts}
\usepackage{mathrsfs}
\usepackage{dsfont}
\usepackage{enumerate}

%\input{../../physics_common.tex}
\input{physics_common.tex}

\title{Tail Indices and Scale Parameters in Financial Time Series}
\author{Thomas Mikosch, Casper de Vries, Xie Xiaolei}
\date{\today}
\begin{document}
\maketitle

\begin{abstract}
We consider an investor with preferences that accord with Generalized
Disappointment Aversion. Such an investor cares about downside risk and
we assume he recognizes the heavy tail feature of asset return
distributions. We argue that when a market is dominated by rational
investors of this kind, the return distributions of equities that are
actively traded in this market must have very similar tail indices. We
also show, in contrast, the scale parameters of the return
distributions may differ hugely from one another.

On the other hand, whether or not all equities in a multivariate model
have the same tail index is a dividing issue for multivariate GARCH
models proposed in the literature. Therefore, it is important to analyze
data of real equity returns and see how close to each other the
tail indices actually are.

In this work empirical results are also presented and they appear
to support the conclusion that the tail indices are very similar,
with respect to the confidence bands of estimation.
\end{abstract}

\section{Introduction}
It is generally believed that the utility function of an
investor is increasing and concave -- as John H. Cochrane
put it, ``the last bite is never as satisfying as the first''
\cite{cochrane2009asset}. This implies investors are repelled to a
larger extent by large losses than they are tempted by large gains. 
Furthermore, it is a stylized fact that equity return distributions
are heavy-tailed (see e.g. Jansen and de Vries \cite{jansen1991frequency}).
In particular, the lower-tail of an equity distribution is often heavier
than the upper-tail of the same distribution.

we explore in this paper the market implications of investor
preferences and the heavy-tail property of equity return
distributions. The rest of this paper is organized into the following
sections:
In section \ref{sec:empirical_results} we present a survey of
statistical characteristics of equity returns. Then 
in section \ref{sec:GDA}, we explicitly recognize the behavioral
concern for downside risk in the investor's evaluation of portfolios
using the framework of Generalized Disappointment Aversion (GDA)
introduced by Routledge and Zin \cite{routledge2010generalized}. GDA
is an extension of the concept of Disappointment Aversion (DA) of Gul
(1991) \cite{gul1991theory}. The Gul paper derives the DA from first
principles (axiomatic).
In this section we infer characteristics of equity returns from the
GDA theory and compare them with the empirical results.

%% Secondly, the empirical fact that the loss return distribution is
%% non-normally fat tailed distributed is taken into account.
%% If investors and speculators alike display concern for downside risk,
%% as formulated by a utility function, it becomes important to model this 
%% risk adequately. see e.g. Jansen and de Vries (1991), exhibiting power
%% like tails rather than exponential tails. The risk is determined both
%% by the coefficient that regulates the hyperbolic power and the
%% scale. We reason how both determine the risk of investment apart from
%% the mean return.

%% \section{Notations}
%% Here is a summary of the notations that we use in the rest of the paper.
%% In this summary $x_F$ denotes a quantity whose value that should be
%% obvious from the context where the notation in question is used.
%% \begin{itemize}
%% \item $\sim$ stands for ``asymptotically equivalent to'', i.e.
%%   $F(x) \sim G(x)$ means
%%   \[
%%   \lim_{x \to x_F} {F(x) \over G(x)} = 1
%%   \]
%% \item $O(F(x))$ stands for terms of the same order as $F(x)$, i.e.
%%   \[
%%   \lim_{x \to x_F } {O(F(x)) \over F(x)} = \text{constant}
%%   \]
%% \item $o(F(x))$ stands for terms of higher orders than $F(x)$, i.e.
%%   \[
%%   \lim_{x \to x_F } {o(F(x)) \over F(x)} = 0
%%   \]
%% \item $\hot$ stands for ``higher order terms'', i.e.
%%   \[
%%   \lim_{x \to x_F} {F(x) + \hot \over F(x)} = 1
%%   \]
%% \end{itemize}

%% \section{Implications of heavy-tailed equity return}
%% \label{sec:1}
%% In this section we consider a rather general utility functional
%% $U(F)$ associated with the distribution function $F(\cdot)$ of
%% an equity return $X$. We define $U(F)$ as
%% \[
%% U(F) = \E u(X)
%% \]
%% for some function $u(\cdot)$ satisfying the following conditions:
%% \begin{enumerate}
%% \item $u(\cdot)$ is defined on $\mathbb R$, is increasing, concave
%%   and differentiable.
%% \item $u(\cdot)$ is independent of the distribution of $X$
%% \item $\lim_{x \to \infty} u(x) = \bar u$, where $\bar u$ is a
%%   constant
%% \end{enumerate}
%% %% An exampple of such utility functions is
%% %% \[
%% %% u(x) = \bar u - e^{-\lambda x}
%% %% \]
%% %% for some $\lambda > 0$.
%% In addition we assume $F(\cdot)$ has the following properties:
%% \begin{enumerate}
%% \item $\lim_{x \to -\infty} F(x) u(x) = 0$
%% \item $\lim_{x \to -\infty} {|x|^\alpha F(x) \over L(|x|)} = 1$
%% \item $\lim_{x \to \infty} {x^\alpha (1 - F(x)) \over L(x)} = 1$
%% \end{enumerate}
%% for some $\alpha > 1$ and some slowly varying function $L(x) > 0$
%% defined on $\mathbb R_+$.
%% $\E u(X)$ can be computed as follows
%% \begin{eqnarray*}
%%   && \E u(X) \\
%%   &=& \int_{-\infty}^{\infty} u(x) d F(x) \\
%%   &=& \left. u(x) F(x) \right|_{-\infty}^{\infty}
%%   - \int_{-\infty}^\infty F(x) u'(x) dx \\
%%   &=& \bar u - \left(
%%   \int_{-\infty}^{-M} + \int_{-M}^{M} + \int_{M}^{\infty}
%%   \right) F(x) u'(x) dx
%% \end{eqnarray*}
%% As $M \to \infty$ we have for the lower-tail integral
%% \begin{eqnarray*}
%%   && \int_{-\infty}^{-M} F(x) u'(x) dx \\
%%   &\sim& \int_{-\infty}^{-M} L(|x|) |x|^{-\alpha} u'(x) dx \\
%%   &=& \int_{M}^{\infty} L(x) x^{-\alpha} u'(-x) dx \\
%% \end{eqnarray*}
%% Applying the same calculation to the upper-tail integral and
%% using $1 - F(x) \sim L(x) x^{-\alpha}$ yields
%% \begin{eqnarray}
%%   && \E u(X) \nonumber \\
%%   &=& \bar u - \int_{M}^\infty L(x) x^{-\alpha} u'(-x) dx
%%   -\int_{-M}^M F(x) u'(x) dx \nonumber \\
%%   && -\int_{M}^\infty [1 - L(x) x^{-\alpha}] u'(x) dx
%%   + \hot \nonumber \\
%%   &=& u(M) - \int_{M}^\infty L(x) x^{-\alpha} [u'(-x) - u'(x)] dx
%%   + \hot \nonumber \\
%%   && - \int_{-M}^M F(x) u'(x) dx \label{eq:xxie0}
%% \end{eqnarray}
%% In the simple case where $L(x) = A$, i.e. a constant, we have
%% \begin{eqnarray}
%%   \pd{\E u(X)}{\alpha} &=& \int_M^{\infty} A x^{-\alpha} \ln(x)
%%      [u'(-x) - u'(x)] dx +\hot \nonumber \\
%%      \pd{\E u(X)}{A} &=& -\int_M^{\infty} x^{-\alpha} [u'(-x) - u'(x)] dx
%%      + \hot
%%   \label{eq:xxie01}   
%% \end{eqnarray}
%% By concavity $u'(-x) > u'(x)$ for $x \in (M, \infty)$. So for large
%% $M$,
%% \[
%% \pd{\E u(X)}{\alpha} > 0, \quad \pd{\E u(X)}{A} < 0
%% \]
%% %% \begin{eqnarray*}
%% %%   \pd{\E u(X)}{\alpha} &>& 0 \\
%% %%   \pd{\E u(X)}{A} &<& 0
%% %% \end{eqnarray*}
%% Now that each and every equity is assigned a score by the utility
%% functional, all equities actively traded in a rational market that
%% is dominated by agents exhibiting a utility function must have almost
%% equal scores -- otherwise trading will be concentrated on those
%% with top scores.

%% Suppose the equity with the highest score in the market has parameters
%% $(\alpha, A)$. We would like to find out how these parameters vary across
%% equities that score almost as high. Consider a parameter pair
%% $(\alpha + \Delta \alpha, A + \Delta A)$. If it scores the same as
%% $(\alpha, A)$, we have
%% \[
%% 0 = \Delta \E u(X) = \Delta \alpha \pd{\E u(X)}{\alpha}
%% + \Delta A \pd{\E u(X)}{A} + \hot
%% \]
%% Discarding higher order terms and plugging \eqref{eq:xxie01} into
%% this equation gives
%% \[
%%   {\Delta \alpha \over \Delta A}
%%   =
%%   {
%%     \int_M^{\infty} x^{-\alpha} [u'(-x) - u'(x)] dx    
%%     \over
%%     \int_M^{\infty} A x^{-\alpha} \ln(x) [u'(-x) - u'(x)] dx    
%%   }
%% \]
%% Taking the limit as $M \to \infty$, we get
%% \[
%% \lim_{M \to \infty} {\Delta \alpha \over \Delta A}
%% =
%% \lim_{M \to \infty} {1 \over A \ln(M)} = 0
%% \]
%% We see from the last equation that in the configuration space around
%% $(\alpha, A)$, a small variation of $\alpha$ induces a tremendous
%% variation of $A$. Furthermore, this conclusion does not depend on the
%% choice of the function $u(\cdot)$. Thus in a market dominated by rational
%% agents guided by their utility functionals, we can expect to see very
%% similar tail indices but hugely different scale parameters in equity
%% return distributions.

%% %% Due to concavity, $u'(-x) > u'(x)$ on the interval $(M, \infty)$.
%% %% The central region integral on $(-M, M)$ does not depend on $\alpha$.
%% %% So $\E u(X)$ is monotonically increasing with $\alpha$. Trying to
%% %% maximize his utility function, an agent will seek the largest $\alpha$
%% %% possible in the market. As a result, all equities traded with significant
%% %% volumes must eventually become so close that they are indistinguishable
%% %% by available statistical methods.

%% In section \ref{sec:GDA}, we compute the utility function within the
%% elaborate framework of {\it Generalized Disappointment Aversion} and
%% show that the same conclusion stands -- tail indices are similar while
%% scale parameters can be drastically different.

\section{Empirical Results}
\label{sec:empirical_results}
As has been mentioned, we are interested in the heavy-tail properties
of equity returns. Let $X_t$ be an equity return series. If the
distribution of $X_t$ is heavy-tailed, we can write
\begin{eqnarray*}
  \lim_{x \to \infty} {x^{\beta}\P(X_t > x) \over L_+(x)} &=& 1 \\
  \lim_{x \to \infty} {x^{\alpha}\P(X_t < -x) \over L_-(x)} &=& 1
\end{eqnarray*}
where the constants $\alpha$ and $\beta$ are left and right tail
indices, respectively, and $L_+(x)$ and $L_-(x)$ are slowly varying
functions satisfying
\[
\lim_{x \to \infty} {L_*(a x) \over L_*(x)} = 1
\]
for all $a > 0$. Here ``*'' can be either ``+'' or ``-''. In the
simplest case, $L_+(x)$ and $L_(x)$ are constants and the distribution
has power-law tails. Let $J_*(1/x) = L_*(x)$. A Taylor expansion at
$x=\infty$ gives
\begin{equation}
  \label{eq:scale_parameter}
  J_*(1/x) = J_*(0) + {J'_*(0) \over x} + O(x^{-2})
\end{equation}
Thus
\begin{equation}
  \label{eq:lower_tail_expansion}
  x^{-\alpha} L_-(x) =
  J_-(0) x^{-\alpha} + J'_-(0) x^{-\alpha - 1} + O(x^{-\alpha-2})
\end{equation}
when $x \to \infty$. Clearly the tail indices $\alpha$ and $\beta$ as
well as the scale parameters $J_-(0)$ and $J_+(0)$ play crutial roles
in determining the tail distribution and hence in asset allocation and
risk management. These parameters of the equities in a market are
characteristics of the market and provide a useful description of the
market. One can also use them to help build a model of the equities in
the market. With these motives in mind, we present a survey of the
tail indices and scale parameters of 3 sectors, namely ``Energy'',
``Consumer Staples'' and ``Information Technology'', of the S\&P 500
index.

\subsection{Hill estimates of lower tail indices}
\label{sec:Hill}
There have been several estimators for the tail index proposed in the
literature, e.g. Hill (1975) \cite{hill1975simple}, Pikands (1975)
\cite{pickands1975statistical}, Dekkers and Einmahl and De Haan (1989)
\cite{dekkers1989moment}. See also Embrechts and Kl\"uppelberg and
Mikosch (1997)\cite{Embrechts1997}. The most popular of these is
arguably Hill (1975) \cite{hill1975simple}:
\begin{equation}
  \label{eq:Hill_index}
  \hat \alpha = \left[
    {1 \over k} \sum_{i=1}^k \ln {x_{(i)} \over x_{(k+1)}}
    \right]^{-1}
\end{equation}
where $x_{(i)}$ is the $i$-th upper order statistic of a sample
$x_1, x_2, ..., x_n$. It has been shown that the Hill estimator is
applicable to 
\begin{itemize}
\item iid random variables (Mason (1982) \cite{mason1982laws})
\item a weakly dependent sequence (Rootz{\'e}n, Leadbetter,
  and de Haan \cite{rootzen1992tail})
\item a linear process (Resnick and St{\u{a}}ric{\u{a}} (1995)
  \cite{resnick1995consistency}).
\end{itemize}
In these cases it is shown that, if $k \to \infty$ and $k/n \to 0$
as $n \to \infty$, the Hill estimator is weakly consistent, i.e.
\[
\sqrt k (\hat \alpha - \alpha) \overset{d}{\to} N(0, \alpha^2)
\]

Figure \ref{fig:Energy_lower},
\ref{fig:Consumer_Staples_lower},
and \ref{fig:Information_Technology_lower}
show the Hill estimates of the
lower tail indices of the ``energy'', ``consumer staples'' and ``information
technology'' sectors of the S\&P 500 index, respectively.
\begin{figure}[htb!]
  \centering
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Energy_lower.pdf}
    \caption{``Energy'' sector of S\&P 500}
    \label{fig:Energy_lower}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Consumer_Staples_lower.pdf}
    \caption{``Consumer Staples'' sector of S\&P 500}
    \label{fig:Consumer_Staples_lower}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Information_Technology_lower.pdf}
    \caption{``Information Technology'' sector of S\&P 500}
    \label{fig:Information_Technology_lower}
  \end{subfigure}
  \caption{\small Hill estimates of lower tail indices of
    daily return series in sectors of Standard \& Poor
    500 index. Each circle coresponds to a Hill estimate; the grey
    triangles above and below it mark the 97.5\% and 2.5\% quantiles
    of its approximate normal distribution.
    The low and high red lines mark the median of the 2.5\% quantiles
    and median of the 97.5\% quantiles, respectively.
    The data are from {\it Yahoo Finance} and the labels on
    the horizontal axis are Yahoo symbols of the stocks. The data span
    from 2010-01-01 to 2015-01-01 and comprise $n=1304$
    observations. $k=50$ lower order statistics are used
    for computing $\alpha_n$. 
  }
\end{figure}
One can see that all the confidence intervals of stocks in the
``Energy'' and ``Consumer Staples'' sectors, as well as those of a
large portion of stocks in the ``Information Technology'' sector,
overlap. This suggests that the stocks in each sector may have very
similar tail indices. Hoga's test on the change of extreme quantiles
may provide some insight about how similar these tail indices are,
because different tail indices are likely to result in different
extreme quantiles. Nevertheless, changes in the extreme quantiles can
be the result of changed tail indices but can also be the result of
changed scale parameters. Thus we first investigate the scale
parameters of stocks in the same sectors before applying Hoga's test.

>>>>

% \documentclass{article}
% \usepackage{amsmath}
% \usepackage{amsthm}
% \usepackage{enumerate}
% \usepackage{bookmark}
% \usepackage{graphicx}
% \usepackage{multirow}
% \usepackage{adjustbox}
% \usepackage{wrapfig}
% \usepackage{subcaption}
% \usepackage{color}
% \usepackage[dvipsnames]{xcolor}

% \usepackage{amssymb,amsmath,amsthm,amsfonts}
% \usepackage{mathrsfs}
% \usepackage{dsfont}
% \usepackage{enumerate}

% \input{physics_common.tex}

\documentclass[11pt,a4]{amsart}
%\usepackage{amsmath}
%\usepackage{amsthm}
%\usepackage{enumerate}
%\usepackage[bookmarks=true]{hyperref}
%\usepackage{bookmark}
\usepackage{graphicx}
\usepackage[bookmarks=true]{ hyperref}
%\usepackage{multirow}
%\usepackage{adjustbox}
%\usepackage{wrapfig}
%\usepackage{subcaption}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}

\usepackage{amssymb,amsmath,amsthm,amsfonts}
%\usepackage{mathrsfs}
%\usepackage{dsfont}
%\usepackage{enumerate}

%\input{../../physics_common.tex}
%\input{physics_common.tex}

\textwidth 6.50in
\topmargin -0.50in
\oddsidemargin 0in
\evensidemargin 0in
\textheight 9.00in
%\pagestyle{plain}
\definecolor{darkblue}{rgb}{.2, 0.2,.8}
\definecolor{darkgreen}{rgb}{0,0.5,0.3}
\definecolor{darkred}{rgb}{.8, .1,.1}
\newcommand{\pd}{\partial}
\newcommand{\red}{\color{darkred}}
\newcommand{\blue}{\color{darkblue}}
\newcommand{\green}{\color{darkgreen}}
\newcommand{\black}{\color{black}}
\newcommand{\levy}{L\'evy}
\newcommand{\slln}{strong law of large numbers}
\newcommand{\clt}{central limit theorem}
\newcommand{\sde}{stochastic \de}
\newcommand{\de}{differential equation}
\newcommand{\mregvar}{multivariate \regvar}
\newcommand{\garch}{{\rm GARCH}$(1,1)$}
\newcommand{\spr}{stochastic process}
\newcommand{\It}{It\^o}
\newcommand{\sta}{St\u aric\u a}
\newcommand{\ex}{{\rm e}\,}
\newcommand{\sas}{s$\alpha$s}
\newcommand{\civ}{\stackrel{v}{\rightarrow}}
\newcommand{\asy}{asymptotic}
\newcommand {\hatt} {\hat{\theta}}
\newcommand {\hattg} {\hat{\theta}_{MLE}}
\newcommand {\hattz} {\hat{\theta}_0}
\newcommand {\hatb} {\hat{\beta}}
\newcommand {\hatbg} {\hat{\beta}_G}
\newcommand {\spp} {^\prime}
\newcommand{\ts}{time series}
\newcommand{\tsa}{\ts\ analysis}
\newcommand{\garchpq}{{\rm GARCH}$(p,q)$}
\def\theequation{\thesection.\arabic{equation}}
\def\tag{\refstepcounter{equation}\leqno }
\def\neqno{\refstepcounter{equation}\leqno(\thesection.\arabic{equation})}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{figur}[lemma]{Figure}
\newtheorem{theorem}[lemma]{Theorem}
\newcommand{\Leb}{{\mathbb L}{\mathbb E}{\mathbb B}}
\newcommand{\bbc}{{\mathbb C}}
\newtheorem{proposition}[lemma]{Proposition}
\newtheorem{definition}[lemma]{Definition}
\newtheorem{corollary}[lemma]{Corollary}
\newtheorem{example}[lemma]{Example}
\newtheorem{exercise}[lemma]{Exercise}
\newtheorem{remark}[lemma]{Remark}
\newtheorem{fig}[lemma]{Figure}
\newtheorem{tab}[lemma]{Table}
\newtheorem{hypothesis}{Hypothesis}
\newcommand{\play}{\displaystyle}
\newcommand{\rmk}{\noindent R{\sc emark}}
\newcommand{\cid}{\stackrel{d}{\rightarrow}}
\newcommand{\cip}{\stackrel{P}{\rightarrow}}
\newcommand{\reference}{\hangindent=5pc\hangafter=1}
\newcommand{\MC}{Markov chain}
\newcommand{\bfQ}{{\bf Q}}
\newcommand{\bfM}{{\bf M}}
\newcommand{\bfu}{{\bf u}}
\newcommand{\bfv}{{\bf v}}
\newcommand{\bfV}{{\bf V}}
\newcommand{\bfU}{{\bf U}}
\newcommand{\bfR}{{\bf R}}
\newcommand{\bfC}{{\bf C}}
\newcommand{\bfF}{{\bf F}}
\newcommand{\RV}{{\rm RV}}
\newcommand{\LN}{{\rm LN}}
\newcommand{\WE}{{\rm WE}}
\newcommand{\bth}{\begin{theorem}}
\newcommand{\ethe}{\end{theorem}}
\newcommand{\sv}{stochastic volatility}
\newcommand{\bre}{\begin{remark}\em }
\newcommand{\ere}{\end{remark}}
\newcommand{\fre}{frequenc}
\newcommand{\ble}{\begin{lemma}}
\newcommand{\ele}{\end{lemma}}
\newcommand{\sre}{stochastic recurrence equation}
\newcommand{\pp}{point process}
\newcommand{\bde}{\begin{definition}}
\newcommand{\ede}{\end{definition}}
\newcommand{\bco}{\begin{corollary}}
\newcommand{\eco}{\end{corollary}}

\newcommand{\bpr}{\begin{proposition}}
\newcommand{\epr}{\end{proposition}}

\newcommand{\bexer}{\begin{exercise}}
\newcommand{\eexer}{\end{exercise}}

\newcommand{\bexam}{\begin{example}}
\newcommand{\eexam}{\end{example}}

\newcommand{\bfi}{\begin{fig}}
\newcommand{\efi}{\end{fig}}

\newcommand{\btab}{\begin{tab}}
\newcommand{\etab}{\end{tab}}
%\renewcommand{\thetab}{\arabic{section}.9.\arabic{tab}}

\newcommand{\edf}{empirical distribution function}
\newcommand{\epro}{empirical process}
\newcommand{\per}{periodogram}
\newcommand{\pf}{{\bf Proof.}}
\newcommand{\lhs}{left-hand side}
\newcommand{\fidi}{finite-dimensional distribution}
\newcommand{\rv}{random variable}
\newcommand{\DA}{{\rm DA}}
\newcommand{\DNA}{{\rm DNA}}
\newcommand{\MDA}{{\rm MDA}}
\newcommand{\sign}{{\rm sign}}
\newcommand{\PRM}{{\rm PRM}}
\newcommand{\card}{{\rm card}}
\newcommand{\var}{{\rm var}}
\newcommand{\med}{{\rm med}}
\newcommand{\cov}{{\rm cov}}
\newcommand{\corr}{{\rm corr}}
\newcommand{\as}{{\rm a.s.}}
\newcommand{\io}{{\rm i.o.}}
\newcommand{\Pois}{\rm Poisson}

\newcommand{\bfth}{\mbox{\boldmath$\theta$}}
\newcommand{\bfTh}{\mbox{\boldmath$\Theta$}}
\newcommand{\bfmu}{\mbox{\boldmath$\mu$}}

\newcommand{\bfvep}{\mbox{\boldmath$\vep$}}
\newcommand{\rhs}{right-hand side}
\newcommand{\df}{distribution function}
\newcommand{\dsum}{\displaystyle\sum}
%\newcommand{\dfrac}{\displaystyle\frac}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\dlim}{\displaystyle\lim\limits}
\newcommand{\dmax}{\displaystyle\max\limits}
\newcommand{\dsup}{\displaystyle\sup\limits}
\newcommand{\dmin}{\displaystyle\min\limits}
\newcommand{\dprod}{\displaystyle\prod}

\newcommand{\beao}{\begin{eqnarray*}}
\newcommand{\eeao}{\end{eqnarray*}\noindent}

\newcommand{\beam}{\begin{eqnarray}}
\newcommand{\eeam}{\end{eqnarray}\noindent}

\newcommand{\beqq}{\begin{equation}}
\newcommand{\eeqq}{\end{equation}\noindent}

\newcommand{\bce}{\begin{center}}
\newcommand{\ece}{\end{center}}

\newcommand{\barr}{\begin{array}}
\newcommand{\earr}{\end{array}}
\newcommand{\cadlag}{c\`adl\`ag}
\newcommand{\tep}{\tilde\epsilon}
\newcommand{\stp}{\stackrel{\P}{\rightarrow}}
\newcommand{\std}{\stackrel{d}{\rightarrow}}
\newcommand{\stas}{\stackrel{\rm a.s.}{\rightarrow}}
\newcommand{\stj}{\stackrel{J_1}{\rightarrow}}
\newcommand{\stv}{\stackrel{v}{\rightarrow}}
\newcommand{\stw}{\stackrel{w}{\rightarrow}}
\newcommand{\stww}{\stackrel{\wh w}{\rightarrow}}
\newcommand{\eqd}{\stackrel{d}{=}}

\newcommand{\refbib}{\cite}
\newcommand{\vague}{\stackrel{\lower0.2ex\hbox{$\scriptscriptstyle
                    \it{v} $}}{\rightarrow}}
\newcommand{\weak}{\stackrel{\lower0.2ex\hbox{$\scriptscriptstyle
                    \it{w} $}}{\rightarrow}}
\newcommand{\what}{\stackrel{\lower0.2ex\hbox{$\scriptscriptstyle
                    \it{\hat{w}} $}}{\rightarrow}}

\newcommand{\bdis}{\begin{displaymath}}
\newcommand{\edis}{\end{displaymath}\noindent}

\newcommand{\Thetabold}{{\boldsymbol{\Theta}}}
\newcommand{\Prob}{\operatorname{P}}
\newcommand{\Dspace}{\mathbb{D}}
\newcommand{\Espace}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Xbold}{{\mathbf{X}}}
\newcommand{\xbold}{{\mathbf{x}}}
\newcommand{\Ybold}{{\mathbf{Y}}}
\newcommand{\ybold}{{\mathbf{y}}}
\newcommand{\zerobold}{{\mathbf{0}}}
\newcommand{\Sphere}{\mathbb{S}}
\newcommand{\Dbar}{\overline{\mathbb{D}}_{0}}
\newcommand{\ind}{independent}
\newcommand{\w}{\omega}
\newcommand{\W}{\Omega}
\newcommand{\bw}{\bigwedge}
\newcommand{\bv}{\bigvee}
\newcommand{\nto}{n\to\infty}
\newcommand{\kto}{k\to\infty}
\newcommand{\xto}{x\to\infty}
\newcommand{\tto}{T\to\infty}
\newcommand{\uto}{u\to\infty}
\newcommand{\ov}{\overline}
\newcommand{\wt}{\widetilde}
\newcommand{\wh}{\widehat}
\newcommand{\vep}{\varepsilon}
\newcommand{\ep}{\epsilon}
\newcommand{\vap}{\varphi}
\newcommand{\la}{\lambda}
\newcommand{\La}{\Lambda}

\newcommand{\halmos}{\hfill \qed}
\newcommand{\regvary}{regularly varying}
\newcommand{\slvary}{slowly varying}
\newcommand{\regvar}{regular variation}
%\newcommand{\bbr}{{I\!\!R}}
%\newcommand{\bbn}{{I\!\!N}}
%\newcommand{\bbz}{{I\!\!\!Z}}

\newcommand{\ka}{\kappa}
\newcommand{\bba}{{\mathcal A}}
\newcommand{\bbe}{{\ov \bbr^{d}_0}}
\newcommand{\bfT}{{\bf T}}
\newcommand{\bbr}{{\mathbb R}}
\newcommand{\bbm}{{\mathcal M}}
\newcommand{\bbb}{{\mathcal B}}
\newcommand{\bbz}{{\mathbb Z}}
\newcommand{\bbn}{{\mathbb N}}
\newcommand{\bbd}{{\mathbb D}}
\newcommand{\bbf}{{\mathcal F}}
\newcommand{\bbs}{{\mathbb S}}
\newcommand{\bbE}{{\mathcal E}}

\newcommand{\BM}{Brownian motion}
\newcommand{\BB}{Brownian bridge}
\newcommand{\con}{convergence}
\newcommand{\ev}{extreme value}
\newcommand{\evt}{extreme value theory}
\newcommand{\evd}{extreme value distribution}
\newcommand{\clp}{central limit problem}
\newcommand{\nc}{norming constant}
\newcommand{\st}{such that}
\newcommand{\fif}{if and only if}
\newcommand{\wrt}{with respect to}
\newcommand{\chf}{characteristic function}
\newcommand{\fct}{function}
\newcommand{\mdoa}{maximum domain of attraction}
\newcommand{\ds}{distribution}
\newcommand{\gev}{generalized extreme value distribution}
\newcommand{\gpd}{generalized Pareto distribution}
\newcommand{\pwm}{probability-weighted moments}
\newcommand{\mle}{maximum likelihood estimator}
\newcommand{\mel}{mean excess function}
\newcommand{\an}{asymptotically normal}
\newcommand{\ac}{absolutely continuous}
\newcommand{\rep}{representation}
\newcommand{\cmt}{continuous mapping theorem}
\newcommand{\seq}{sequence}
\newcommand{\pr} {{\bf Proof.}}
\newcommand{\ins}{insurance}
\newcommand{\mat}{mathematic}
\newcommand{\pro}{probabilit}
\newcommand{\pros}{probabilities}
\newcommand{\ms}{measure}
\newcommand{\mgf}{moment generating function}
\newcommand{\ld}{large deviation}
\newcommand{\bfx}{{\bf x}}
\newcommand{\bfX}{{\bf X}}
\newcommand{\bfB}{{\bf B}}
\newcommand{\bfY}{{\bf Y}}
\newcommand{\bfy}{{\bf y}}
\newcommand{\bfA}{{\bf A}}
\newcommand{\bfG}{{\bf G}}
\newcommand{\bfO}{{\bf 0}}
\newcommand{\bfZ}{{\bf Z}}
\newcommand{\bfz}{{\bf z}}
\newcommand{\bfS}{{\bf S}}
\newcommand{\bfa}{{\bf a}}
\newcommand{\bfb}{{\bf b}}
\newcommand{\bfe}{{\bf e}}
\newcommand{\bft}{{\bf t}}
\newcommand{\bfI}{{\bf I}}
\newcommand{\bfs}{{\bf s}}
\newcommand{\bfh}{{\bf h}}
\newcommand{\bfunit}{{\bf h}}
\newcommand{\ARCH}{{\rm ARCH}}
\newcommand{\E }{{\mathbb E}}
\renewcommand{\P }{{\mathbb P}}
\newcommand{\Q }{{\mathbb Q}}
\newcommand{\1}{{\mathbf 1}}

\newcommand{\floor}[1]{
  \lfloor #1\rfloor
}
\newcommand{\ceil}[1]{
  \lceil #1\rceil
}

\allowdisplaybreaks
\begin{document}
\title{Tail-indices and scale parameters of returns series}
\author{Thomas Mikosch,  Casper de Vries, Xie Xiaolei, }
\date{\today}

\maketitle

\begin{abstract}
%We consider an investor with preferences that accord with Generalized
%Disappointment Aversion. Such an investor cares about downside risk and
%we assume he recognizes the heavy tail feature of asset return
%distributions. We argue that when a market is dominated by rational
%investors of this kind, the return distributions of equities that are
%actively traded in this market must have very similar tail indices. We
%also show, in contrast, the scale parameters of the return
%distributions may differ hugely from one another.
%On the other hand, whether or not all equities in a multivariate model
%have the same tail index is a dividing issue for multivariate GARCH
%models proposed in the literature. Therefore, it is important to analyze
%data of real equity returns and see how close to each other the
%tail indices actually are.
%In this work empirical results are also presented and they appear
%to support the conclusion that the tail indices are very similar,
%with respect to the confidence bands of estimation.
\end{abstract}

\section{Introduction}\setcounter{equation}{0}
It is one of the stylized facts of financial econometrics that 
returns of speculative prices are {\em heavy-tailed.} There is no agreement
in the literature how heavy tails really are. For example, Barndorff-Nielsen and Shephard
\cite{barndorff:shephard:2001} and Eberlein \cite{eberlein:2001} favor ``semi-heavy'' tails, i.e.,
tails which are comparable with those of a gamma \ds . On the other
hand, tails of returns have been studied in great detail 
in the extreme value community. Among extreme value specialists
there is general agreement that returns $X_t$ have tails of power-law-type, i.e.,
\beam\label{eq:1}
\P(X_t>x)\sim c_+ \,x^{\alpha_{\rm up}}\quad\mbox{and}\quad \P(X_t<-x)\sim c_-\,x^{-\alpha_{\rm low}}\,,\quad\xto\,,
\eeam  
where $c_{\pm}$ are positive constants.\footnote{Here and in what
  follows, $f(x)\sim g(x)$ for positive \fct s $f$ and $g$ means 
that $f(x)/g(x)\to 1$ as $\xto$.} See for example, Embrechts et
al. \cite{embrechts:klueppelberg:mikosch:1997}, Jansen and de Vries
\cite{jansen1991frequency}, Mikosch \cite{mikosch:2003}, Resnick
\cite{resnick:2007}.  
In the extreme value literature it is common to replace the constants $c_\pm$ by a suitable
{\em slowly varying} \fct s; cf. Embrechts et
al. \cite{embrechts:klueppelberg:mikosch:1997}, Chapter 3. In this
paper, for the  
sake of argument, we stick to the condition \eqref{eq:1}.
\par
There are some good theoretical reasons for the appearance of power-law tails in situations where certain moments 
of data are believed to be infinite. Tails of the type \eqref{eq:1}
describe the maximum domain of attraction of the  
Fr\'echet \ds\ $\Phi_\alpha(x)=\exp(-x^{-\alpha})$ for $x>0$. Equivalently, power-law tails are prescribed by the 
generalized Pareto \ds\ which is the limit \ds\ of the excesses of $X_t$ above high thresholds, i.e.,
\beao
\P((X_t-u)/a(u)>x \mid X_t>x) \to (1+ x/\alpha)^{-\alpha}\,,\qquad u\to\infty\,.
\eeao
The aforementioned results 
are considered very natural for iid and weakly dependent strictly stationary \seq s of random variables $(X_t)$; 
in the world of extremes they are the analogs
of the \clt\ from the world of sums.
\par
In the literature on extremes for return data one finds the 
statement that {\em estimated} values $\hat \alpha_{\rm up}$ and $\hat \alpha_{\rm low}$ 
of the tail-indices $\alpha_{\rm up}$ and $\alpha_{\rm low}$,
respectively, typically have the tendency that $\hat \alpha_{\rm
  up}>\hat \alpha_{\rm low}$. 
This observation is often explained by the fact that investors are
more prone to negative than to positive news in te market. 
Moreover, in the literature the {\em estimated} tail-indices $\hat \alpha$ (both in the left and right tails) 
are typically found in the range $(2.5,4)$. For an illustration, see
